%\chapter*{\large СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ}
\begin{thebibliography}{99}

\bibitem{KG} Shamir A. How to share a secret / A. Shamir // Communications of the ACM. --- 1979. --- Vol. 22, No. 11. --- P. 612--613.

\bibitem{VSS} Pedersen T.P. A Threshold Cryptosystem without a Trusted Party / T.P. Pedersen // Advances in Cryptology --- EUROCRYPT '91 / ed. by D.W. Davies. --- Berlin, Heidelberg: Springer, 1991. --- Vol. 547. Lecture Notes in Computer Science. --- P. 522--526.

\bibitem{Gen} R. Gennaro S. Jarecki H. Krawczyk and T. Rabin. Secure distributed key generation for discrete-log based cryptosystems. In Eurocrypt '99, pages 295-310, 1999.

\bibitem{Fel} P. Feldman. A practical scheme for non-interactive verifiable secret sharing. In 28th FOCS, pages 427-437, 1987.

\bibitem{Schnorr} C. P. Schnorr. Efficient signature generation by smart cards. Journal of Cryptology, 4:161-174, 1991.  

\bibitem{SS} Douglas R. Stinson and Reto Strobl. Provably Secure Distributed Schnorr Signatures and a (\textit{t, n}) Threshold Scheme for Implicit Certificates. In Proceedings of the 6th Australian Conference on Information Security and Privacy, ACISP'01, pages 417-434, 2001.

\bibitem{ROM} Агиевич С. В. Схема подписи Шнорра [Электронный ресурс] : лекционные материалы / С. В. Агиевич. --- Белорусский государственный университет, 2012. --- Режим доступа: https://apmi.bsu.by/assets/files/agievich/schnorr.pdf. --- Дата обращения: 09.11.2025.

\bibitem{FROST} C. Komlo and I. Goldberg. FROST: flexible round-optimized Schnorr threshold signatures. In O. Dunkelman, M. J. J. Jr., and C. O’Flynn, editors, Selected Areas in Cryptography - SAC 2020 - 27th International Conference, Halifax, NS, Canada (Virtual Event), October 21-23, 2020, Revised Selected Papers, volume
12804 of Lecture Notes in Computer Science, pages 34–65. Springer, 2020.

\bibitem{ZKP} Агиевич С. В. Доказательства с нулевым разглашением [Электронный ресурс] : лекционные материалы / С. В. Агиевич. --- Белорусский государственный университет, 2012. --- Режим доступа: https://apmi.bsu.by/assets/files/agievich/zkp.pdf. --- Дата обращения: 09.11.2025.

\bibitem{Dr}Dan Boneh, Manu Drijvers, and Gregory Neven. Compact Multi-signatures for
Smaller Blockchains. In ASIACRYPT, pages 435–464, 2018.

\bibitem{BD} D. Wagner. A Generalized Birthday Problem. In CRYPTO, 2002.

\end{thebibliography}
\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ}